Bacterial Microbiome and Obesity Meta-analysis Statistics Pipeline

### 2016-02-05 code/StatisticsProcessing.Rmd
updated statistics

test2 <- test[keep, ]
good.metadata <- test2
rm(metadata, test, test2)

metadata <- good.metadata[!grepl("_s2", good.metadata$submitted_sample_id_s),]
keep <- rownames(metadata)
microbiome <- shared.data[keep, ]
rm(good.metadata, shared.data, keep)

@@

anova(lm(H ~ obese)) #P-value=0.2145
anova(lm(S ~ obese)) #P-value=0.05925
anova(lm(J ~ obese)) #P-value=0.5093

@@

anova(lm(bacter ~ obese)) #P-value=0.9485
anova(lm(firm ~ obese)) #P-value=0.2379
anova(lm(BFratio ~ obese)) #P-value=0.9277

@@

set.seed(3)
adonis(microbiome ~ obese, permutations=1000) 
#PERMANOVA=0.5504, pseudo-F=0.97273

@@

##Shannon Diversity
H.cat <- alpha.test$shannon.cat
S.cat <- alpha.test$S.cat
J.cat <- alpha.test$J.cat
bmi.cat <- as.character(obese)
test3 <- cbind(H.cat, S.cat, J.cat, bmi.cat)
test3 <- test3[order(H.cat), ]
table(test3[c(1:100), 4])
table(test3[c(101:201), 4])
#Group1 (Higher than median), obese = 29 and non-obese = 71
#Group2 (Lower than median), obese = 45 and non-obese = 56

group1 <- c(29, 71)
group2 <- c(45, 56)
r.test <- rbind(group2, group1)
colnames(r.test) <- c("Obese", "Not.Obese")
rownames(r.test) <- c("group2", "group1")

epi.2by2(r.test, method="cohort.count")
## Risk Ratio = 1.54
## CI = 1.05, 2.24
## p-value = 0.022

@@

median(BFRatio$BFRatio) # 0.537415
BFRatio <- within(BFRatio, {BFRatio.cat = ifelse(BFRatio <= median(BFRatio), "less", "higher")})

BFRatio.cat <- BFRatio$BFRatio.cat
test4 <- cbind(BFRatio.cat, obese)
test4 <- test4[order(BFRatio.cat), ]
table(test4[c(1:100), 2]) #higher group
table(test4[c(101:201), 2]) #lower group
#Group1 (Higher than median), obese = 38 and non-obese = 62
#Group2 (Lower than median), obese = 36 and non-obese = 65

group1 <- c(38, 62)
group2 <- c(36, 65)
r.test <- rbind(group2, group1)
colnames(r.test) <- c("Obese", "Not.Obese")
rownames(r.test) <- c("group2", "group1")

epi.2by2(r.test, method="cohort.count")
## Risk Ratio = 0.94
## CI = 0.65, 1.35
## p-value = 0.729

@@

#Try AUCRF with default measures provided in readme
set.seed(3)
fit <- AUCRF(obese ~ ., data=testset, ntree=1000, nodesize=20)
summary(fit) # list of 32 Measures, AUCopt = 0.6679613
plot(fit)
```

@@

StudyNo <- c(1, 2, 3, 4, 5, 6, 7, 8)
Study <- c("Baxter", "HMP", "Ross", "Escobar", "Argumugam", "Turnbaugh", "Zupancic", "Wu")
Year <- c("2015", "2011", "2015", "2014", "2010", "2009", "2012", "2012")
Total <- c("n=172", "n=256", "n=63", "n=30", "n=85", "n=146", "n=201", "n=58")
tpos <- c(25, 16, 20, 6, 20, 52, 45, 2) #obese in low diversity group
tneg <- c(61, 112, 12, 9, 23, 21, 56, 27) #nonobese in low diversity group
cpos <- c(22, 10, 18, 4, 17, 47, 29, 3) #obese in high diversity group
cneg <- c(64, 118, 13, 11, 25, 26, 71, 26) #nonobese in high diversity group
RR <- c(1.14, 1.6, 1.08, 1.50, 1.15, 1.11, 1.54, 0.67)
low <- c(0.70, 0.75, 0.72, 0.53, 0.71, 0.88, 1.05, 0.12)
high <- c(1.85, 3.39, 1.61, 4.26, 1.87, 1.38, 2.24, 3.70)

@@

## Alternative way - 
# Seems easier to follow plus I am not trying to do
# a meta analysis on a model

data <-as.data.frame(cbind(RR, low, high))
raw.overall2 <- as.data.frame(cbind(Study,Year, data))

raw.overall2$logRR <- log(raw.overall2$RR)
raw.overall2$SE <- (log(raw.overall2$high) - log(raw.overall2$low))/(2*1.96)
attach(raw.overall2)
metaplot(logRR, SE, labels=Study, nn=1, logeffect=TRUE, col=meta.colors("black"), xlab="RR of Obesity in high versus low Shannon diversity based on Median", ylab="")
  #Graphical output is not as informative

##Calculate combined P-value
m = 8
T = -2*log(0.608)-2*log(0.214)-2*log(0.236)-2*log(0.439)-2*log(0.575)-2*log(0.376)-2*log(0.022)-2*log(0.64)
T.pval = 1-pchisq(T,m) #P-value = 0.01

##Alternatively can use built in package (I trust this more)
anova.rma(res)
# QM = 5.0973, p-value = 0.0240

@@

StudyNo <- c(1, 2, 3, 4, 5, 6, 7, 8)
Study <- c("Baxter", "HMP", "Ross", "Escobar", "Argumugam", "Turnbaugh", "Zupancic", "Wu")
Year <- c("2015", "2011", "2015", "2014", "2010", "2009", "2012", "2012")
Total <- c("n=172", "n=256", "n=63", "n=30", "n=85", "n=146", "n=201", "n=58")
tpos <- c(24, 13, 16, 3, 17, 45, 36, 2) #obese in low BF group
tneg <- c(62, 115, 16, 12, 26, 28, 65, 27) #nonobese in low BF group
cpos <- c(23, 13, 22, 7, 20, 54, 38, 3) #obese in high BF group
cneg <- c(63, 115, 9, 8, 22, 19, 62, 26) #nonobese in high BF group
RR <- c(1.04, 1.00, 0.70, 0.43, 0.83, 0.83, 0.94, 0.67)
low <- c(0.64, 0.48, 0.47, 0.14, 0.51, 0.66, 0.65, 0.12)
high <- c(1.70, 2.07, 1.07, 1.35, 1.35, 1.05, 1.35, 3.70)

@@

##Calculate combined P-value
m = 8
T = -2*log(0.864)-2*log(1.00)-2*log(0.089)-2*log(0.121)-2*log(0.452)-2*log(0.111)-2*log(0.729)-2*log(0.64)
T.pval = 1-pchisq(T,m) #P-value = 0.03155827

##Alternatively can use built in package (I trust this more)
anova.rma(res)
  # QM = 4.8452, p-value = 0.0277

@@

## Load in libraries to be used as well as directory with the data
library(ggplot2)
library(plyr)
library(reshape2)
library(RColorBrewer)
library(scales)
library(pheatmap)
library(gridExtra)

@@

#Amish STD = 0.6010608
amish.ZScore.H <- amish.data$H.corr/0.6010608
hist(amish.ZScore.H)
#Turnbaugh STD = 0.4818751
turn.ZScore.H <- turn.data$H.corr/0.4818751
hist(turn.ZScore.H)
#MetaHit-Den STD = 0.4038558
keepmetahit <- which(data1$dataset == "MetaHit")
metahitdata <- data1[keepmetahit, ]
metahit.ZScore.H <- metahitdata$H.corr/0.4038558
hist(metahit.ZScore.H)
#Korean STD = 0.5400615
keepKorean <- which(data1$dataset == "Korean")
Koreandata <- data1[keepKorean, ]
Korean.ZScore.H <- Koreandata$H.corr/0.5400615
hist(Korean.ZScore.H)
#HMP STD = 0.6774514
keepHMP <- which(data1$dataset == "HMP")
hmpdata <- data1[keepHMP, ]
HMP.ZScore.H <- hmpdata$H.corr/0.6774514
hist(HMP.ZScore.H)
#CCHC STD = 0.5784522
keepCCHC <- which(data1$dataset == "CCHC")
CCHCdata <- data1[keepCCHC, ]
CCHC.ZScore.H <- CCHCdata$H.corr/0.5784522
hist(CCHC.ZScore.H)
#GLNE07 STD = 0.4663871
keepGLNE <- which(data1$dataset == "GLNE")
GLNEdata <- data1[keepGLNE, ]
GLNE.ZScore.H <- GLNEdata$H.corr/0.4663871
hist(GLNE.ZScore.H)
#Escobar STD = 0.5378935
keepescobar <- which(data1$dataset == "Escobar")
escobardata <- data1[keepescobar, ]
Escobar.ZScore.H <- escobardata$H.corr/0.5378935
hist(Escobar.ZScore.H)
#COMBO STD = 0.6870763
keepCOMBO <- which(data1$dataset == "COMBO")
COMBOdata <- data1[keepCOMBO, ]
COMBO.ZScore.H <- COMBOdata$H.corr/0.6870763
hist(COMBO.ZScore.H)

@@

group.data.test1 <- cbind(comb1.H.Zscore, comb1.obese, comb1.bmi.class)
group.data.test2 <- cbind(comb2.H.Zscore, comb2.obese)
colnames(group.data.test1) <- c("H.Zscore", "obese", "BMI.class")
colnames(group.data.test2) <- c("H.Zscore", "obese")
#Look at Obese versus non-obese
t.test(H.Zscore ~ obese, data=group.data.test2) #P-value = 0.002792
table(group.data.test2$obese) # No = 693 | Yes = 336
p1 <- ggplot(group.data.test2, aes(obese, H.Zscore)) + geom_boxplot()

@@

#Amish SD = 0.7990372
am.BF.corr <- as.character(amish.data$BF.ratio.corr)
am.BF.corr <- as.numeric(am.BF.corr) # Value 19 has no value
amish.norm.BF <- am.BF.corr/0.7990372
hist(amish.norm.BF)
#Turnbaugh SD = 0.4578937
turn.norm.BF <- turn.data$BF.corr/0.4578937
hist(turn.norm.BF)
#MetaHit SD = 0.9707577
keepmetahit <- which(data2$dataset == "MetaHit")
metahitdata <- data2[keepmetahit, ]
metahit.norm.BF <- metahitdata$BF.ratio.corr/0.9707577
hist(metahit.norm.BF)
#Korean SD = 0.6048195
keepKorean <- which(data2$dataset == "Korean")
Koreandata <- data2[keepKorean, ]
Korean.norm.BF <- Koreandata$BF.ratio.corr/0.6048195
hist(Korean.norm.BF)
#HMP SD = 8.301864
keepHMP <- which(data2$dataset == "HMP")
hmpdata <- data2[keepHMP, ]
HMP.norm.BF <- hmpdata$BF.ratio.corr/8.301864
hist(HMP.norm.BF)
#CCHC SD = 2.00527
keepCCHC <- which(data2$dataset == "CCHC")
CCHCdata <- data2[keepCCHC, ]
CCHC.norm.BF <- CCHCdata$BF.ratio.corr/2.00527
hist(CCHC.norm.BF)
#GLNE07 SD = 0.4451074
keepGLNE <- which(data2$dataset == "GLNE")
GLNEdata <- data2[keepGLNE, ]
GLNE.norm.BF <- GLNEdata$BF.ratio.corr/0.4451074
hist(GLNE.norm.BF)
#Escobar SD = 0.4232106
keepescobar <- which(data2$dataset == "Escobar")
escobardata <- data2[keepescobar, ]
Escobar.norm.BF <- escobardata$BF.ratio.corr/0.4232106
hist(Escobar.norm.BF)
#COMBO SD = 5.928664
keepCOMBO <- which(data2$dataset == "COMBO")
COMBOdata <- data2[keepCOMBO, ]
COMBO.norm.BF <- COMBOdata$BF.ratio.corr/5.928664
hist(COMBO.norm.BF)

@@

#Look at Obese versus non-obese
t.test(BF.ratio.corr ~ obese, data=group.data.test2) 
  # P-value = 0.05066
table(group.data.test2$obese)
  # No = 693 | Yes = 336
bf1 <- ggplot(group.data.test2, aes(obese, BF.ratio.corr)) + geom_boxplot()

@@

###################################Bacteroidetes#######################################
#Look at Obese versus non-obese
t.test(Zbacter ~ obese, data=group.data.test2) 
  # P-value = 0.3161
table(group.data.test2$obese)
  # No = 693 | Yes = 336
bacter1 <- ggplot(group.data.test2, aes(obese, Zbacter)) + geom_boxplot()

@@

###################################Firmicutes#######################################
#Look at Obese versus non-obese
t.test(Zfirm ~ obese, data=group.data.test2) #P-value = 0.8298
table(group.data.test2$obese)
  # No = 693 | Yes = 336
firm1 <- ggplot(group.data.test2, aes(obese, Zfirm)) + geom_boxplot()

@@

###################################Bacteroidetes/Firmicutes#######################################
#Look at Obese versus non-obese
t.test(zbf ~ obese, data=group.data.test2) #P-value = 0.4167
table(group.data.test2$obese)
  # No = 693 | Yes = 336
zbf1 <- ggplot(group.data.test2, aes(obese, zbf)) + geom_boxplot()

>>>>

test2 <- test[keep, ]
good.metadata <- test2
test3 <- test2[!duplicated(test2$submitted_subject_id_s), ]
keep <- rownames(test3)
microbiome <- shared.data[keep, ]
metadata <- test3

rm(good.metadata, shared.data, keep, test, test2, test3)

@@

anova(lm(H ~ obese)) #P-value=0.2034
anova(lm(S ~ obese)) #P-value=0.03516
anova(lm(J ~ obese)) #P-value=0.5369

@@

anova(lm(bacter ~ obese)) #P-value=0.9582
anova(lm(firm ~ obese)) #P-value=0.2654
anova(lm(BFratio ~ obese)) #P-value=0.9899

@@

set.seed(3)
adonis(microbiome ~ obese, permutations=1000) 
#PERMANOVA=0.5734, pseudo-F=0.95626

@@

##Shannon Diversity
H.cat <- alpha.test$shannon.cat
S.cat <- alpha.test$S.cat
J.cat <- alpha.test$J.cat
bmi.cat <- as.character(obese)
test3 <- cbind(H.cat, S.cat, J.cat, bmi.cat)
test3 <- test3[order(H.cat), ]
table(test3[c(1:103), 4])
table(test3[c(104:207), 4])
#Group1 (Higher than median), obese = 31 and non-obese = 72
#Group2 (Lower than median), obese = 47 and non-obese = 57

group1 <- c(31, 72)
group2 <- c(47, 57)
r.test <- rbind(group2, group1)
colnames(r.test) <- c("Obese", "Not.Obese")
rownames(r.test) <- c("group2", "group1")

epi.2by2(r.test, method="cohort.count")
## Risk Ratio = 1.50
## CI = 1.04, 2.16
## p-value = 0.025

@@

median(BFRatio$BFRatio) # 0.5414258
BFRatio <- within(BFRatio, {BFRatio.cat = ifelse(BFRatio <= median(BFRatio), "less", "higher")})

BFRatio.cat <- BFRatio$BFRatio.cat
test4 <- cbind(BFRatio.cat, obese)
test4 <- test4[order(BFRatio.cat), ]
table(test4[c(1:103), 2]) #higher group
table(test4[c(104:207), 2]) #lower group
#Group1 (Higher than median), obese = 41 and non-obese = 62
#Group2 (Lower than median), obese = 37 and non-obese = 67

group1 <- c(41, 62)
group2 <- c(37, 67)
r.test <- rbind(group2, group1)
colnames(r.test) <- c("Obese", "Not.Obese")
rownames(r.test) <- c("group2", "group1")

epi.2by2(r.test, method="cohort.count")
## Risk Ratio = 0.89
## CI = 0.66, 1.27
## p-value = 0.53

@@

#Try AUCRF with default measures provided in readme
set.seed(3)
fit <- AUCRF(obese ~ ., data=testset, ntree=1000, nodesize=20)
summary(fit) # list of 42 Measures, AUCopt = 0.6365534
plot(fit)
```

@@

StudyNo <- c(1, 2, 3, 4, 5, 6, 7, 8)
Study <- c("Baxter", "HMP", "Ross", "Escobar", "Arumugam", "Turnbaugh", "Zupancic", "Wu")
Year <- c("2015", "2011", "2015", "2014", "2010", "2009", "2012", "2012")
Total <- c("n=172", "n=256", "n=63", "n=30", "n=85", "n=146", "n=207", "n=58")
tpos <- c(25, 16, 20, 6, 20, 52, 47, 2) #obese in low diversity group
tneg <- c(61, 112, 12, 9, 23, 21, 57, 27) #nonobese in low diversity group
cpos <- c(22, 10, 18, 4, 17, 47, 31, 3) #obese in high diversity group
cneg <- c(64, 118, 13, 11, 25, 26, 72, 26) #nonobese in high diversity group
RR <- c(1.14, 1.6, 1.08, 1.50, 1.15, 1.11, 1.50, 0.67)
low <- c(0.70, 0.75, 0.72, 0.53, 0.71, 0.88, 1.04, 0.12)
high <- c(1.85, 3.39, 1.61, 4.26, 1.87, 1.38, 2.16, 3.70)

@@

##Calculate combined P-value
m = 8
T = -2*log(0.608)-2*log(0.214)-2*log(0.236)-2*log(0.439)-2*log(0.575)-2*log(0.376)-2*log(0.025)-2*log(0.64)
T.pval = 1-pchisq(T,m) #P-value = 0.01

##Alternatively can use built in package (I trust this more)
anova.rma(res)
# QM = 5.1101, p-value = 0.0238

@@

StudyNo <- c(1, 2, 3, 4, 5, 6, 7, 8)
Study <- c("Baxter", "HMP", "Ross", "Escobar", "Arumugam", "Turnbaugh", "Zupancic", "Wu")
Year <- c("2015", "2011", "2015", "2014", "2010", "2009", "2012", "2012")
Total <- c("n=172", "n=256", "n=63", "n=30", "n=85", "n=146", "n=207", "n=58")
tpos <- c(24, 13, 16, 3, 17, 45, 37, 2) #obese in low BF group
tneg <- c(62, 115, 16, 12, 26, 28, 67, 27) #nonobese in low BF group
cpos <- c(23, 13, 22, 7, 20, 54, 41, 3) #obese in high BF group
cneg <- c(63, 115, 9, 8, 22, 19, 62, 26) #nonobese in high BF group
RR <- c(1.04, 1.00, 0.70, 0.43, 0.83, 0.83, 0.89, 0.67)
low <- c(0.64, 0.48, 0.47, 0.14, 0.51, 0.66, 0.66, 0.12)
high <- c(1.70, 2.07, 1.07, 1.35, 1.35, 1.05, 1.27, 3.70)

@@

##Calculate combined P-value
m = 8
T = -2*log(0.864)-2*log(1.00)-2*log(0.089)-2*log(0.121)-2*log(0.452)-2*log(0.111)-2*log(0.53)-2*log(0.64)
T.pval = 1-pchisq(T,m) #P-value = 0.03155827

##Alternatively can use built in package (I trust this more)
anova.rma(res)
  # QM = 5.3494, p-value = 0.0207

@@

library(ggplot2)
library(plyr)
library(reshape2)
library(RColorBrewer)
library(scales)
library(pheatmap)
library(gridExtra)

@@

#Amish STD = 0.5893173
amish.ZScore.H <- amish.data$H.corr/0.5893173
hist(amish.ZScore.H)
#Turnbaugh STD = 0.4818751
turn.ZScore.H <- turn.data$H.corr/0.4818751
hist(turn.ZScore.H)
#MetaHit-Den STD = 0.4038558
keepmetahit <- which(data1$dataset == "MetaHit")
metahitdata <- data1[keepmetahit, ]
metahit.ZScore.H <- metahitdata$H.corr/0.4038558
hist(metahit.ZScore.H)
#Korean STD = 0.5400615
keepKorean <- which(data1$dataset == "Korean")
Koreandata <- data1[keepKorean, ]
Korean.ZScore.H <- Koreandata$H.corr/0.5400615
hist(Korean.ZScore.H)
#HMP STD = 0.6774514
keepHMP <- which(data1$dataset == "HMP")
hmpdata <- data1[keepHMP, ]
HMP.ZScore.H <- hmpdata$H.corr/0.6774514
hist(HMP.ZScore.H)
#CCHC STD = 0.5784522
keepCCHC <- which(data1$dataset == "CCHC")
CCHCdata <- data1[keepCCHC, ]
CCHC.ZScore.H <- CCHCdata$H.corr/0.5784522
hist(CCHC.ZScore.H)
#GLNE07 STD = 0.4663871
keepGLNE <- which(data1$dataset == "GLNE")
GLNEdata <- data1[keepGLNE, ]
GLNE.ZScore.H <- GLNEdata$H.corr/0.4663871
hist(GLNE.ZScore.H)
#Escobar STD = 0.5378935
keepescobar <- which(data1$dataset == "Escobar")
escobardata <- data1[keepescobar, ]
Escobar.ZScore.H <- escobardata$H.corr/0.5378935
hist(Escobar.ZScore.H)
#COMBO STD = 0.6870763
keepCOMBO <- which(data1$dataset == "COMBO")
COMBOdata <- data1[keepCOMBO, ]
COMBO.ZScore.H <- COMBOdata$H.corr/0.6870763
hist(COMBO.ZScore.H)

@@

group.data.test1 <- cbind(comb1.H.Zscore, comb1.obese, comb1.bmi.class)
group.data.test2 <- cbind(comb2.H.Zscore, comb2.obese)
colnames(group.data.test1) <- c("H.Zscore", "obese", "BMI.class")
colnames(group.data.test2) <- c("H.Zscore", "obese")
#Look at Obese versus non-obese
t.test(H.Zscore ~ obese, data=group.data.test2) #P-value = 0.002583
table(group.data.test2$obese) # No = 695 | Yes = 340
p1 <- ggplot(group.data.test2, aes(obese, H.Zscore)) + geom_boxplot()

@@

#Amish SD = 0.7918527
am.BF.corr <- as.character(amish.data$BF.ratio.corr)
am.BF.corr <- as.numeric(am.BF.corr) # Value 19 has no value
amish.norm.BF <- am.BF.corr/0.7918527
hist(amish.norm.BF)
#Turnbaugh SD = 0.4578937
turn.norm.BF <- turn.data$BF.corr/0.4578937
hist(turn.norm.BF)
#MetaHit SD = 0.9707577
keepmetahit <- which(data2$dataset == "MetaHit")
metahitdata <- data2[keepmetahit, ]
metahit.norm.BF <- metahitdata$BF.ratio.corr/0.9707577
hist(metahit.norm.BF)
#Korean SD = 0.6048195
keepKorean <- which(data2$dataset == "Korean")
Koreandata <- data2[keepKorean, ]
Korean.norm.BF <- Koreandata$BF.ratio.corr/0.6048195
hist(Korean.norm.BF)
#HMP SD = 8.301864
keepHMP <- which(data2$dataset == "HMP")
hmpdata <- data2[keepHMP, ]
HMP.norm.BF <- hmpdata$BF.ratio.corr/8.301864
hist(HMP.norm.BF)
#CCHC SD = 2.00527
keepCCHC <- which(data2$dataset == "CCHC")
CCHCdata <- data2[keepCCHC, ]
CCHC.norm.BF <- CCHCdata$BF.ratio.corr/2.00527
hist(CCHC.norm.BF)
#GLNE07 SD = 0.4451074
keepGLNE <- which(data2$dataset == "GLNE")
GLNEdata <- data2[keepGLNE, ]
GLNE.norm.BF <- GLNEdata$BF.ratio.corr/0.4451074
hist(GLNE.norm.BF)
#Escobar SD = 0.4232106
keepescobar <- which(data2$dataset == "Escobar")
escobardata <- data2[keepescobar, ]
Escobar.norm.BF <- escobardata$BF.ratio.corr/0.4232106
hist(Escobar.norm.BF)
#COMBO SD = 5.928664
keepCOMBO <- which(data2$dataset == "COMBO")
COMBOdata <- data2[keepCOMBO, ]
COMBO.norm.BF <- COMBOdata$BF.ratio.corr/5.928664
hist(COMBO.norm.BF)

@@

#Look at Obese versus non-obese
t.test(BF.ratio.corr ~ obese, data=group.data.test2) 
  # P-value = 0.0525
table(group.data.test2$obese)
  # No = 695 | Yes = 340
bf1 <- ggplot(group.data.test2, aes(obese, BF.ratio.corr)) + geom_boxplot()

@@

###################################Bacteroidetes#######################################
#Look at Obese versus non-obese
t.test(Zbacter ~ obese, data=group.data.test2) 
  # P-value = 0.3202
table(group.data.test2$obese)
  # No = 695 | Yes = 340
bacter1 <- ggplot(group.data.test2, aes(obese, Zbacter)) + geom_boxplot()

@@

###################################Firmicutes#######################################
#Look at Obese versus non-obese
t.test(Zfirm ~ obese, data=group.data.test2) #P-value = 0.8149
table(group.data.test2$obese)
  # No = 695 | Yes = 340
firm1 <- ggplot(group.data.test2, aes(obese, Zfirm)) + geom_boxplot()

@@

###################################Bacteroidetes/Firmicutes#######################################
#Look at Obese versus non-obese
t.test(zbf ~ obese, data=group.data.test2) #P-value = 0.4379
table(group.data.test2$obese)
  # No = 695 | Yes = 340
zbf1 <- ggplot(group.data.test2, aes(obese, zbf)) + geom_boxplot()
